---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# gameoflife

<!-- badges: start -->
<!-- badges: end -->

The goal of gameoflife is to ...

## Development

To load the package for development in RStudio or RStudio Server, create a new project in RStudio using the "Create Project from Version Control" option. Select "Git" and use the repository URL:

`https://github.com/alexcodreanu86/code-retreat/`

If you are using RStudio Server, you should "Create project as subdirectory of" `~/repos`.

If you aren't an RStudio fan you can use `git clone`.

To load the current state of the package for development, ensure that your working directory is set to `~/repos/code-retreat/R/gameoflife`, and call the following functions from the console:

``` {r dev eval=FALSE}
devtools::document() # this generates documentation from any markdown you have defined
devtools::load_all() # this attaches the complete package namespace, including non-exported functions
```

Attaching the package using `load_all()` is preferable to assigning individual objects in the global environment during development.

To run tests that you have defined with `testthat`, run:

```{r test eval=FALSE}
devtools::test() # this is a convenient wrapper for testthat::test_dir
```

## Dependencies

You may be accustomed to writing scripts that attach third party packages using `library()`.

In package development, you should specify dependencies by naming them in the DESCRIPTION file in the package root.

Example:

```{r imports eval=FALSE}
Imports: 
    dplyr
    purrr
```

Objects exported by packages named `Imports` will not be made available directly to the package's users when your package is installed, but code in your own package can use them.

`https://kbroman.org/pkg_primer/pages/depends.html` gives a good rundown of how to handle dependencies in package development.

## Installation

You can install the released version of gameoflife from [CRAN](https://CRAN.R-project.org) with:

``` {r gol1}
install.packages("gameoflife")
```

And the development version from [GitHub](https://github.com/) with:

``` {r gol2}
# install.packages("devtools")
devtools::install_github("alexcodreanu86/code-retreat")
```
